\section{Related Work}
As a new switching technology which has not been standardized yet, OBS faces many problems and challenges. However, there are also many researchers and new achievements. In resolving the issues of contention and the associated loss bursts issue. There are some other related studies. 

The most important and related study is contention resolution. As mention above, there are three ways to resolve burst contention. Fiber delay line, wavelength conversion and deflection routing by now. They are for a same goal. When contention occurs, they can buffer it instead of drop it. But these three method are not viable now. They all have their own shortcomings. Optical buffering currently can only be implemented using FDL. But this type of optical buffer is
usually small and it does not scale up. The wavelength may have some potential since the number of wavelengths that can be coupled together onto a single fiber continues to increase. In view of deflected routing, the end-to-end delay for an optical burst may be unacceptably high. But fortunately research on these contention resolution are going on. Once the breakthrough of these problems will also provide help for congestion control. 

Nowadays, IP packet switching already dominates global communications. But it cannot keep up with the Internet traffic demand. Many researchers are studying a new scheme to replace it. In electronic domain, ATM network has matured and is not far from being feasible. Other researcher have proposed integrate circuit switching in the core and packet switching in the edges as next generation network architecture. All of these efforts are aimed at accommodating for the traffic growth in the Internet. Study on the OBS can draw on
their achievements. Also include conventional TCP congestion control. 
