% Thesis Acknowledgements ------------------------------------------------


%\begin{acknowledgementslong} %uncommenting this line, gives a different acknowledgements heading
\begin{acknowledgements}      %this creates the heading for the acknowlegments

First and foremost I offer my sincerest gratitude to my supervisor, Dr. Conor McArdle, who has supported me throughout my thesis with his patience and knowledge whilst allowing me the room to work in my own way. I attribute the level of my Masters degree to his encouragement and effort and without him this thesis,too,would not have been completed or written. One simply could not wish for a better or friendlier supervisor.

Thanks are also due to Prof. Tommy Curran for supporting this work to date,etc. I am also greatly indebted to the professors and teachers at the school of electronic engineering: Dr. Martin Collier, Dr. Jennifer McManis, Dr. Gabriel-Miro Muntean, who have instructed and helped me a lot in the past years. Especially, I would like to express my appreciation to Dr. Derek Molloy for preparing the original version of this template document.   

Last my thanks would go to my beloved family for their loving considerations and great confidence in me all through these years. I also owe my sincere gratitude to my friends and my fellow classmates who gave me their help and time in listening to me and helping me work out my problems during the difficult course of the thesis.

Last but not least, I would like to thank those who relly made it possible for me to do my master at DCU because of their encouragement and emotional support.

\end{acknowledgements}
%\end{acknowledgmentslong}

% ------------------------------------------------------------------------

%%% Local Variables: 
%%% mode: latex
%%% TeX-master: "../thesis"
%%% End: 
