\section{Summary}

Overview the history of the development of OBS technology. The original goal is to compete with ATM network which have great potential in electronic domain. Compared with primitive Burst switching, ATM is more cost effective. But when WDM technology can provide huge bandwidth. It posed a challenge to current switch technology, that is how to use this bandwidth efficiently. The switch technology become the network bottleneck. OBS is a new technology that is currently
under study. It has not as yet been commercialized and standardized. But It has great potential to replace current switch technology. It has some advantages:

\begin{enumerate}
    \item More flexible and efficient compared with wavelength routed network
    \item More scalable and cost effective compared with opto-electronic approaches
    \item Smaller overhead and more practical compared with OPS
\end{enumerate}

It also have some prominent feature:

\begin{enumerate}

    \item Separation of transmission and control, Each user transmits data in bursts
    \item Basically, assumes the network is bufferless
    \item Network nodes(OXC) allocate resources for just this single burst

\end{enumerate}

By contrast, we can find that OBS has a lot of advantages for packet switch. However, unfortunately contention is inherent to the OBS technique. The contention problem is due to the lack of information at the nodes and the absence of global coordination between the edge routers and core routers. In one word, I want to proposed a new scheme to avoid and control congestion effectively in this study. And then drive OBS into standardized earlier.
